Supplementary Materials

### 2023-05-12 results_discussion.tex
Add pseudocounts for plotting dseq

% Software comparison table
\begin{table}[!ht]
\centering
\input{figures/table-comp}
 \caption{COATi generates better alignments than other alignment algorithms. Results of COATi, PRANK, MAFFT, Clustal$\Omega$, and MACSE aligning 7719 empirically simulated sequence pairs. Perfect alignments have $d_{seq}=0$, best alignments have the lowest $d_{seq}$, and imperfect alignments have $d_{seq}>0$ when at least one aligner found a perfect alignment.}
 \label{table:comp}
\end{table}

COATi, using the codon-triplet-ecm model, was significantly more accurate (lower $d_{seq}$) at inferring simulated alignments compared to other methods; all p-values were less than $4.0 \cdot 10^{-06}$ according to the one-tailed Wilcoxon signed rank test.
In addition, COATi produced more perfect alignments, less imperfect alignments, and more accurately retrieved events of positive selection (Table \ref{table:comp}).
It obtained better results compared to a wide variety of alignment strategies.
Clustal$\Omega$, performing a common approach of aligning via amino acid translations, obtained the highest average alignment error and had difficulties retrieving positive selection.
MACSE, which allows frameshifts, is also based on an amino acid model and obtained similar results to the DNA-based MAFFT.
PRANK, using a codon model, had a similar average alignment error to MACSE and MAFFT but had issues recovering the simulated alignments.

>>>>

% Software comparison table
\begin{table}[!ht]
\centering
\input{figures/table-comp}
 \vspace{1mm}
 \footnotesize{* PRANK produced 50 empty alignments, calculations are based on 7869 alignments.}
 \caption{COATi generates better alignments than other alignment algorithms. Results of COATi, PRANK, MAFFT, Clustal$\Omega$, and MACSE aligning 7719 empirically simulated sequence pairs. Perfect alignments have $d_{seq}=0$, best alignments have the lowest $d_{seq}$, and imperfect alignments have $d_{seq}>0$ when at least one aligner found a perfect alignment. Alignments with equal score to the true alignment are considered perfect.}
 \label{table:comp}
\end{table}

COATi, using the codon-triplet-ecm model, was significantly more accurate (lower $d_{seq}$) at inferring simulated alignments compared to other methods; all p-values were less than $2.06 \cdot 10^{-79}$ according to the one-tailed Wilcoxon signed rank test.
In addition, COATi produced more perfect alignments, less imperfect alignments, and more accurately retrieved events of positive selection (Table \ref{table:comp}).
It obtained better results compared to a wide variety of alignment strategies.
Clustal$\Omega$, performing a common approach of aligning via amino acid translations, obtained the highest average alignment error and had difficulties retrieving positive selection.
MACSE, which allows frameshifts, is also based on an amino acid model and obtained similar results to the DNA-based MAFFT.
PRANK, using a codon model, had a similar average alignment error to MACSE and MAFFT but had issues recovering the simulated alignments.
